% **************************************************************************************************************
% A Classic Thesis Style
% An Homage to The Elements of Typographic Style
%
% Copyright (C) 2018 André Miede and Ivo Pletikosić
%
% If you like the style then I would appreciate a postcard. My address
% can be found in the file ClassicThesis.pdf. A collection of the
% postcards I received so far is available online at
% http://postcards.miede.de
%
% License:
% This program is free software; you can redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation; either version 2 of the License, or
% (at your option) any later version.
%
% This program is distributed in the hope that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
%
% You should have received a copy of the GNU General Public License
% along with this program; see the file COPYING.  If not, write to
% the Free Software Foundation, Inc., 59 Temple Place - Suite 330,
% Boston, MA 02111-1307, USA.
%
% PLEASE SEE ALSO THE AUTHORS' NOTE REGARDING THIS LICENSE
% IN THE DOCUMENTATION (ClassicThesis.pdf --> Chapter 1 / Chapter01.tex)
% **************************************************************************************************************
\RequirePackage{silence} % :-\
    \WarningFilter{scrreprt}{Usage of package `titlesec'}
    %\WarningFilter{scrreprt}{Activating an ugly workaround}
    \WarningFilter{titlesec}{Non standard sectioning command detected}
\documentclass[ twoside,openright,titlepage,numbers=noenddot,%1headlines,
                headinclude,footinclude,cleardoublepage=empty,abstract=on,
                BCOR=5mm,paper=a4,fontsize=11pt
                ]{scrreprt}

%********************************************************************
% Note: Make all your adjustments in here
%*******************************************************
\input{classicthesis-config}

%********************************************************************
% Bibliographies
%*******************************************************
\addbibresource{Bibliography.bib}
\addbibresource[label=ownpubs]{AMiede_Publications.bib}

%********************************************************************
% Hyphenation
%*******************************************************
%\hyphenation{put special hyphenation here}

% ********************************************************************
% GO!GO!GO! MOVE IT!
%*******************************************************
\begin{document}
\frenchspacing
\raggedbottom
\selectlanguage{american} % american ngerman
%\renewcommand*{\bibname}{new name}
%\setbibpreamble{}
\pagenumbering{roman}
\pagestyle{plain}
%********************************************************************
% Frontmatter
%*******************************************************
%\include{FrontBackmatter/DirtyTitlepage}
\include{FrontBackmatter/Titlepage}
\include{FrontBackmatter/Titleback}
\cleardoublepage\include{FrontBackmatter/Dedication}
%\cleardoublepage\include{FrontBackmatter/Foreword}
\cleardoublepage\include{FrontBackmatter/Abstract}
%\cleardoublepage\include{FrontBackmatter/Publications}
\cleardoublepage\include{FrontBackmatter/Acknowledgments}
\cleardoublepage\include{FrontBackmatter/Contents}
%********************************************************************
% Mainmatter
%*******************************************************
\cleardoublepage
\pagestyle{scrheadings}
\pagenumbering{arabic}
%\setcounter{page}{90}
% use \cleardoublepage here to avoid problems with pdfbookmark
\cleardoublepage
\ctparttext{This first part serves as an introduction to both the LHC and the CMS experiment, their design and their applications. We also discuss the problem of \emph{event simulation} in HEP, revising the current state-of-the-art procedure along with its main characteristics and limitations. The following two chapters are intended for putting into context the work done in this thesis.

Chapter 1 may be safely skipped if the reader has already a basic understanding of the LHC and a general-purpose apparatus such as CMS. The latter part of the chapter is the most significant, as it present the process chosen as benchmark for our simulation approach. Chapter 2 presents the specific approach to simulation and data formats taken by CMS, a necessary background for understanding the advances presented in this work.}
\part{Introduction and Problem overview}\label{pt:probover}
\include{Chapters/Chapter01}
\include{Chapters/Chapter02}
\cleardoublepage
\ctparttext{We move on to describe the building blocks of our work, i.e. \emph{Deep Learning} and specifically \emph{Generative Models}. We conclude with a discussion about the powerful approach know as \emph{Normalizing Flows}. 

Chapter 3 serves as an high level introduction to the field, and may be safely skipped if the reader is already acquainted with it. Chapter 4 discusses in greater detail a specific and less well-known ML algorithm for data generation which allowed us to derive the results of the latter part of this work.}
\part{Tools}\label{pt:tools}
%\addtocontents{toc}{\protect\clearpage} % <--- just debug stuff, ignore
\include{Chapters/Chapter03}
\include{Chapters/Chapter04}
\cleardoublepage
\ctparttext{This final part presents the original contribution resulting fro  this Thesis work. In chapter 5 we discuss the practical implementation and setup and show that our approach to simulation is capable of producing high-quality data samples with \emph{several orders of magnitude of speedup} when compared to FullSim.

Chapter 6 shows that we can actually employ our generated data for performing a MC-based analysis, specifically the VBF Channel of H$\rightarrow\mu^+\mu^-$.

Finally, Chapter 7 draws a conclusion of the present work, discussing some possible future research directions.}
\part{Thesis contribution}\label{pt:thcont}
\include{Chapters/Chapter05}
\include{Chapters/Chapter06}
\include{Chapters/Chapter07}
%\include{multiToC} % <--- just debug stuff, ignore for your documents
% ********************************************************************
% Backmatter
%*******************************************************
\appendix
%\renewcommand{\thechapter}{\alph{chapter}}
\cleardoublepage
\ctparttext{You can put some informational part preamble text here.
Illo principalmente su nos. Non message \emph{occidental} angloromanic
da. Debitas effortio simplificate sia se, auxiliar summarios da que,
se avantiate publicationes via. Pan in terra summarios, capital
interlingua se que. Al via multo esser specimen, campo responder que
da. Le usate medical addresses pro, europa origine sanctificate nos se.}
\part{Appendix}
\include{Chapters/Chapter0A}
%********************************************************************
% Other Stuff in the Back
%*******************************************************
\cleardoublepage\include{FrontBackmatter/Bibliography}
\cleardoublepage\include{FrontBackmatter/Declaration}
\cleardoublepage\include{FrontBackmatter/Colophon}
% ********************************************************************
% Game Over: Restore, Restart, or Quit?
%*******************************************************
\end{document}
% ********************************************************************
