%********************************************************************
% Appendix
%*******************************************************
% If problems with the headers: get headings in appendix etc. right
%\markboth{\spacedlowsmallcaps{Appendix}}{\spacedlowsmallcaps{Appendix}}
\chapter{Appendix Test}\label{ch:appx}
First of all, we point out to the interested reader that the final version of the code used in this Thesis is hosted and documented in detail online \href{tbd}{at the following repository}\footnote{repository link, tbd}.

\section{Extraction and preprocessing}
With the use of \texttt{C/C++} code (name of script) for the \texttt{ROOT} data analysis framework \cite{Brun:491486}, we processed the NanoAOD files and extracted all the Jet objects matched to a GenJet object and the Muon objects matched to a GenMuon across all the events in the file. This operation can be performed rather quickly thanks to the \emph{compiled} language being used and the powerful \texttt{ROOT::RDataFrame()} class, offering a modern, high-level interface for the manipulation of data stored in a NanoAOD \texttt{TTree}, as well as \emph{multi-threading} and other low-level optimisations.
The output of the \emph{extraction} step is another \texttt{.root} file containing just the selected objects.

 We thus open the \texttt{.root} file directly in a \texttt{Python} script through the \texttt{uproot} package \cite{jim_pivarski_2022_6791281}, discard the Events structure to obtain a simple table with one object per line, perform the preprocessing as discussed above and save the output in \texttt{.hdf5} format for the training.

\section{Appendix Section Test}
Test: \autoref{tab:moreexample} (This reference should have a
lowercase, small caps \spacedlowsmallcaps{A} if the option
\texttt{floatperchapter} is activated, just as in the table itself
 $\rightarrow$ however, this does not work at the moment.)

\begin{table}[h]
    \myfloatalign
    \begin{tabularx}{\textwidth}{Xll} \toprule
        \tableheadline{labitur bonorum pri no} & \tableheadline{que vista}
        & \tableheadline{human} \\ \midrule
        fastidii ea ius & germano &  demonstratea \\
        suscipit instructior & titulo & personas \\
        %postulant quo & westeuropee & sanctificatec \\
        \midrule
        quaestio philosophia & facto & demonstrated \\
        %autem vulputate ex & parola & romanic \\
        %usu mucius iisque & studio & sanctificatef \\
        \bottomrule
    \end{tabularx}
    \caption[Autem usu id]{Autem usu id.}
    \label{tab:moreexample}
\end{table}

%Nulla fastidii ea ius, exerci suscipit instructior te nam, in ullum
%postulant quo. Congue quaestio philosophia his at, sea odio autem
%vulputate ex. Cu usu mucius iisque voluptua. Sit maiorum propriae at,
%ea cum primis intellegat. Hinc cotidieque reprehendunt eu nec. Autem
%timeam deleniti usu id, in nec nibh altera.




\section{Another Appendix Section Test}
Equidem detraxit cu nam, vix eu delenit periculis. Eos ut vero
constituto, no vidit propriae complectitur sea. Diceret nonummy in
has, no qui eligendi recteque consetetur. Mel eu dictas suscipiantur,
et sed placerat oporteat. At ipsum electram mei, ad aeque atomorum
mea. There is also a useless Pascal listing below: \autoref{lst:useless}.

\begin{lstlisting}[float=b,language=Pascal,frame=tb,caption={A floating example (\texttt{listings} manual)},label=lst:useless]
for i:=maxint downto 0 do
begin
{ do nothing }
end;
\end{lstlisting}

%Ei solet nemore consectetuer nam. Ad eam porro impetus, te choro omnes
%evertitur mel. Molestie conclusionemque vel at, no qui omittam
%expetenda efficiendi. Eu quo nobis offendit, verterem scriptorem ne
%vix.

